High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-04 notebooks/mnist.qmd
additional models

>>>>

#### Additional Models (not in paper)

```{julia}
add_retrain = true

# Deep Ensemble:
mlp_large_ens = EnsembleModel(model=mlp, n=50)

add_models = Dict(
    "Large MLP Ensemble" => mlp_large_ens,
)

if add_retrain
    add_model_dict = Dict(mod_name => _train(mod; mod_name=mod_name) for (mod_name, mod) in add_models)
    large_model_dict = merge(model_dict, add_model_dict)
    Serialization.serialize(joinpath(output_path,"mnist_models_large.jls"), large_model_dict)
else
    large_model_dict = Serialization.deserialize(joinpath(output_path,"mnist_models_large.jls"))
end
```

```{julia}
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = ["MLP", "MLP Ensemble", "Large Ensemble" "JEM", "JEM Ensemble"]
)
display(plt_additional_models)
savefig(plt, joinpath(output_images_path, "mnist_eccco_additional.png"))
```
